The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-25 paper/sections/methods.tex
deformation origins

\subsection{Choosing Deformation Origins}
\label{sec:origins}
% \dave{Ty: try to follow this formula when writing 
% \dave{maybe this should come after weight computation ?}
% (1) what is the purpose of this part of the method ?
% (2) what are the criteria for success
% (3) what is our assumed input 
% (4) what is the desired output
% (5) what's the algorith,
% (6) add proofs/diagrams/figures that show we satisfy (2). }
To ensure kinematic expressiveness, it is essential that multiple origins of deformation are permitted. Each part, $\prt_i$, must be associated with a single deformation origin, $\bar{\refX}_j$. Each origin is computed as the centroid of the set of parts with which it is associated. While we constrain a part to be paired with only one deformation origin, an origin may be associated any number of parts. Next, we require that each deformation origin be associated with a minimum of two parts, which avoids the case of an origin laying on the surface of a part.\ty{Should we mention periodic surfaces? You can have a periodic nurbs sphere consisting of a single surface, which we couldn't handle with this constraint (easy fix, but not sure if worth mentioning)} Furthermore, we seek that the sparsity of the deformation origins mirrors that of the blending weights. Intuitively, this means that for a region in which weights are high for a subset of parts, the origin of deformation should be centered in this region.

\begin{figure}[h]
    \includegraphics[width=\columnwidth]{figures/origin_network}
    \caption{Example structure for the network flow selection of deformation origins with a shape consisting of three parts. Red arrows indicate each parts origin association.}
    \label{fig:network_flow}
\end{figure}

From the set of blending weights we seek to construct a set of candidate deformation origins and then produce a set of deformation origins, $\XBs$, adhering to the outlined requirements. This set of candidate origins is identified by examining the unique combinations of weight assignments for the quadrature points. For each $\refX_j$, we form a set $\mathbf{b}\left(\refX_j\right)$ with $b_i\left(\refX_j\right)= 1-\delta_{\bld_i\left(\refX_j\right),0}$ where $\delta_{x,0}$ is the Kronecker delta. This produces a binary code for each quadrature point that identifies the parts to which this point has nonzero weights. We use each unique binary code as a deformation origin candidate.

With the set of requirements and candidate origins, we see this problem may be organized in a graph structure ~(\reffig{network_flow}) where the relationships between parts and deformation origins can be realized as a bipartite graph. We exploit this structure by forming a min-cost-flow problem that produces a solution satisfying the requirements.

Consider a directed bipartite graph $G=(V = A \cup B,E)$ where each node in $A$ corresponds to a deformation origin candidate and each node in $B$ represents a part. $E$ is the set of edges connecting nodes in $A$ to $B$ where each origin has an edge to every part with which it attempts to associate. We augment $G$ to form $G'=(V' = A \cup B \cup \{s,t\}, E')$ where $V'$  is the new set of nodes now containing the source, $s$, and sink, $t$, nodes. $E'$ is the augmented set of nodes connecting $s$ to each candidate in $A$ and connecting each part in $B$ to the sink $t$. Each edge $(i,j) \in E'$ has an associated flow $f_{ij}$ and capacity constraint $u_{ij}$, and each edge in $E$ also has a cost $c_{ij}$. The principal constraint for this network flow problem is the conservation constraint, meaning that the net flow for all nodes in $V$ is zero.

Next, we constrain all flow values to be integral and place a capacity of $1$ on the edges from $B$ to $t$. This has the effect of enforcing that any part node in $B$ receives flow from a single edge, and as a consequence each part may only be associated with a single deformation origin. The last step is to specify the costs on the edges, $E$, between the origin candidates and the parts. Costs are assigned in such a way that for each unique binary code, $\mathbf{b}$, we sum the set of weights for each quadrature point associated with this code. Since for each non-zero $b_i$, we have an edge connecting the node corresponding to $\mathbf{b}$ to the $i$-th part in $A$, we take the $i$-th sum to be the cost for this edge. \ty{Need to think how to rewrite this}. The resulting sum has a nonzero value With the specified network and constraints, we solve this problem with an integer constrained linear program. We choose $\XBs$ to be all the deformation origin candidates in $A$ that have an outgoing flow of at least $1$.

\subsection{Meshless Integration}

We integrate physical quantities over our undeformed object using raycasting based quadrature~\cite{KHOSRAVIFARD201030}.

>>>>

\subsection{Choosing Deformation Origins}
\label{sec:origins}
% \dave{Ty: try to follow this formula when writing 
% \dave{maybe this should come after weight computation ?}
% (1) what is the purpose of this part of the method ?
% (2) what are the criteria for success
% (3) what is our assumed input 
% (4) what is the desired output
% (5) what's the algorith,
% (6) add proofs/diagrams/figures that show we satisfy (2). }
Each part, $\prt_i$, must be associated with a single deformation origin, $\bar{\refX}_j$. 
Each origin is computed as the centroid of the set of parts with which it is associated. 
While we constrain a part to be paired with only one deformation origin, an origin may be associated any number of parts. 
Further, we require that each deformation origin be associated with a minimum of two parts, which avoids the case of an origin laying on the surface of a part.\ty{Should we mention periodic surfaces? You can have a periodic nurbs sphere consisting of a single surface, which we couldn't handle with this constraint (easy fix, but not sure if worth mentioning)}\dave{yes} 
Finally, to avoid unduly coupling the parts and reducing the expressivity of the simulation, we seek a sparse association of origins 
which mirrors the pointwise sparsity of our blending weights,

%of the blending weights. Intuitively, this means that for a region in which weights are high for a subset of parts, the origin of deformation should be centered in this region.

\begin{figure}[h]
    \includegraphics[width=\columnwidth]{figures/origin_network}
    \caption{Example structure for the network flow selection of deformation origins with a shape consisting of three parts. Red arrows indicate each parts origin association. \dave{make it clear edges of triangle are sep. parts}}
    \label{fig:network_flow} 
\end{figure}

Candidate deformation origins are selected by clustering quadrature points~(\refsec{quadrature}).
We group quadrature points by the combination of parts influencing each point (non-zero blending weight~(\refsec{weights})).
Each group now represents a unique part combination and the centroid of these parts becomes a deformation origin candidate.
To assign deformation origins to parts we use an integer network flow approach~\dave{cite}~(\reffig{origin_network}).

Consider a directed bipartite graph $G=(V = A \cup B,E)$ where each node in $A$ corresponds to a deformation origin candidate and each node in $B$ represents to a part. 
$E$ is the set of edges connecting nodes in $A$ to $B$ where each origin has an edge to every part with which it attempts to associate. 
We augment $G$ to form $G'=(V' = A \cup B \cup \{s,t\}, E')$ where $V'$  is the new set of nodes now containing the source, $s$, and sink, $t$. $E'$ is the augmented set of nodes connecting $s$ to each candidate in $A$ and connecting each part in $B$ to the sink $t$. Each edge $(i,j) \in E'$ has an associated flow $f_{ij}$ and capacity constraint $u_{ij}$, and each edge in $E$ also has a cost $c_{ij}$. The principal constraint for this network flow problem is the conservation constraint, meaning that the net flow for all nodes in $V$ is zero.\dave{B is really overloaded}
Each edge from from $B$ to $t$ is assigned a capacity of $1$, which enforces that any part node in $B$ receives flow from a single edge, 
and as a consequence each part may only be associated with a single deformation origin. 
The last step is to specify the costs on the edges, $E$, between the origin candidates and the parts.

Given a quadrature point group, and an edge from the associated deformation origin to $\prt_i$, we set the edge capacity to be the sum, 
over all quadrature points in the group, of the blending weights associated with $\prt_i$.
This capacity causes more heavily ``connected'' origin candidates to be selected. 
We solve this problem with an integer constrained linear program\dave{cite solver} and choose $\XBs$ to be all the deformation origin candidates in $A$ 
that have an outgoing flow of at least $1$. 
This approach chooses deformation origins that satisfy our stated criteria.

\subsection{Meshless Integration}
\label{sec:quadrature}
We integrate physical quantities over our undeformed object using raycasting based quadrature~\cite{KHOSRAVIFARD201030}.
